Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-01 paper/paper.tex
pass

\subsection{Discussion}
\label{sec:rce}
\label{sec:jboss}
\label{sec:content-example}
\label{sec:dos}

\subsubsection{Lack of comparison with other tools}
Table~\ref{table:comparison} summarizes the characteristics of
alternative techniques and provides details about the evaluation used
in their original paper. Unfortunately, side comparison was not
possible for three key reasons. First, we did not have access to the
tools. We tried, unsuccssefully, making contact with authors to obtain
the tools. Second, the tools output different objects. For that
reason, a comparison based on published results did not make sense. It
is important to recall that we did not report precision and recall as
it is 100\% always. \tname captures, by construction, all positive
traffic and does not capture any negative traffic. We used a stronger
criteria instead---the position of the correct rule in the ranking. It
is possible that other rules, higher in the ranking, are useful, but
only domain experts can identify that. Third, we are the only
technique to support content options, which are prevalent and
challenging to handle. A side comparison would be unfair if we
consider rules with those options.

@@

%% \textbf{'content' option support.} Another limitation is the support of 'content' option. Most papers do not support rule generation with the 'content' option, using only classic DDoS attacks in the rule generation, like ICMP and SYN flood, which only use numerical and categorical options. Some papers do support 'content', but don't explain well how they handle those rules with exclusive 'content'.}
%%  \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
%%  evolutionaries approaches to 
%% autonomously generate rules using the Snort IDS. They built 
%% their own ICMP datasets by using packet creation tools or by capturing network traffic. 
%% Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
%% for non-ICMP attacks.
%% 
%% Vollmer created ten different packets to match ten existing rules, and then used 
%% these packets as input to the rule generation process. As a result, the produced 
%% rules achieved a 100\% detection rate and produced 3 false positives out of 33k packets.
%% 
%% Guruprasad manually created a set of rules by analyzing the network patterns and 
%% the datasets, this set of rules was used as the initial population of the algorithm. 
%% The produced rules achieved a detection rate up to 96\%, the false positive rate 
%% was not evaluated. 
%% 
%% On our experiments with Syrius, we used a total of \totalPackets packets that 
%% matches \totalAttacks different existing rules and it was able to generate rules that detected 
%% all the packets with no false positives.  
%%  }  
\subsubsection{Running time}\Mar{}\Gui{We ran all our tests using an Intel(R) Xeon(R) CPU E3-1240 v6 and 8GB RAM. For attacks with only categorical and numerical options, the average running time was 6 seconds per attack. For attacks with the content option, the average running time was 1445 seconds.}

@@

\subsection{Threats to Validity}
\label{sec:threats}

Our experiments is affected by the usual threats. Considering external
validity. Our results cannot be generalized beyond the subjects we
selected. To mitigate that threat we selected a variety of attacks
with different characteristics. Unfortunately, we could not access
tools for related techniques. For that reason, we made a
side-comparison based on the common examples and results reported in
the original paper. Considering internal validity, the implementation
of \tname\ could contain errors. We mitigated that threat by carefully
inspecting code and results. Considering construct validity, the
choice of ranking to evaluate the approach may not be useful in
practice. We considered the use of ranking of the golden rule a
reasonable choice as the approach places the golden rule close to the
top in most cases.

>>>>

%\subsection{Threats to Validity}

\subsection{Discussion}
\label{sec:rce}
\label{sec:jboss}
\label{sec:content-example}
\label{sec:dos}
\label{sec:threats}

%\subsubsection{Lack of comparison with other tools}
\noindent\textbf{Lack of comparison with other tools}
Table~\ref{table:comparison} summarizes the characteristics of
alternative techniques and provides details about the evaluation used
in corresponding papers. Unfortunately, side comparison was not
possible for three key reasons. First, we did not have access to the
tools. We tried, unsuccssefully, making contact with authors to obtain
the tools. Second, the tools output different objects. For that
reason, a comparison based on published results did not make sense. It
is important to recall that we did not report precision and recall as
it is 100\% always. \tname captures, by construction, all positive
traffic and does not capture any negative traffic. We used a stronger
criteria instead---the position of the correct rule in the ranking. It
is possible that other rules, higher in the ranking, are useful, but
only domain experts can identify that. Third, we are the only
technique to support content options, which are prevalent and
challenging to handle. A side comparison would be unfair if we
consider rules with those options.
\noindent\textbf{Running times.}~We ran all our tests using an
Intel(R) Xeon(R) CPU E3-1240 v6 and 8GB RAM. For attacks with only
categorical and numerical options, the average running time was 6
seconds per attack. For attacks with the content option, the average
running time was 1,445 seconds (=24.1 minutes).  \textbf{Threats to
  Validity.}~Considering external validity. Our results cannot be
generalized beyond the subjects we selected. To mitigate that threat
we selected a variety of attacks with different
characteristics. Unfortunately, we could not access tools for related
techniques, but there is strong evidence that \tname\ performs very
well and is the only technique to support content options, which are
very important in this domain. Considering internal validity, in
principle, the implementation of \tname\ could contain errors. We
mitigated that threat by carefully inspecting code and
results. Considering construct validity, the choice of ranking to
evaluate the approach may not be useful in practice. We considered the
use of ranking of the golden rule a reasonable choice as the approach
places the golden rule close to the top in most cases.

% For that reason, we made a side-comparison based on the common
% examples and results reported in the original paper.

@@

%% \textbf{'content' option support.} Another limitation is the support of 'content' option. Most papers do not support rule generation with the 'content' option, using only classic DDoS attacks in the rule generation, like ICMP and SYN flood, which only use numerical and categorical options. Some papers do support 'content', but don't explain well how they handle those rules with exclusive 'content'.}
%%  \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
%%  evolutionaries approaches to 
%% autonomously generate rules using the Snort IDS. They built 
%% their own ICMP datasets by using packet creation tools or by capturing network traffic. 
%% Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
%% for non-ICMP attacks.
%% 
%% Vollmer created ten different packets to match ten existing rules, and then used 
%% these packets as input to the rule generation process. As a result, the produced 
%% rules achieved a 100\% detection rate and produced 3 false positives out of 33k packets.
%% 
%% Guruprasad manually created a set of rules by analyzing the network patterns and 
%% the datasets, this set of rules was used as the initial population of the algorithm. 
%% The produced rules achieved a detection rate up to 96\%, the false positive rate 
%% was not evaluated. 
%% 
%% On our experiments with Syrius, we used a total of \totalPackets packets that 
%% matches \totalAttacks different existing rules and it was able to generate rules that detected 
%% all the packets with no false positives.  
%%  }

@@
